
#Replication of "How Will I Be Remembered? Conserving the Environment for the Sake of One's Legacy" by Zaval, Markowitz & Weber (2015, Psychological Science)
##Rhia Catapano


##Introduction

Although encouraging pro-environmental behaviors is extremely important to the future, there are a number of psychological barriers that can prevent pro-environmental behaviors. Specifically, the long time horizon and psychological distance serve as barriers to this important goal. The current paper looks to leverage these elements of pro-environmental behavior into opportunities, rather than barriers. 

Specifically, the paper finds that priming legacy motives increased donations to an enviromnmental charity, proenvironmental intentions, and climate change beliefs. To prime legacy motives, participants write about what they want to be remembered for by future generations. This increases motivation to leave a positive legacy, which in turn increases pro-environmental behaviors. Therefore, this paper uses a simple intervention to leverage a major barrier in environmental behavior (future-focused and distant) into an opportunity to encourage these behaviors.

##Methods

###Power Analysis

The original study reports cohen's d's ranging from 0.23 to 0.36 on the various measures used (legacy motives, climate change beliefs, behavioral intentions, and donation measure). Therefore, I've assumed a cohen's d of 0.23, to be conservative. The standard deviation for most of the measures is approximately 1.

```{r power95}
power.t.test(delta=0.23, sd=1, power=.95, sig.level=0.05)
```
```{r power90}
power.t.test(delta=0.23, sd=1, power=.90, sig.level=0.05)
```
```{r power80}
power.t.test(delta=0.23, sd=1, power=.80, sig.level=0.05)
```


###Planned Sample
The original paper uses a sample size of about 300 participants, based on the estimated effect size from a pilot test. This is around the number of participants required for 80% power, and is the most feasible number of participants that will not severely underpower the study.


###Materials & Procedure

**Writing activity**
Participants will be randomly assigned to one of two conditions. As per the original experiment, "In the legacy condition, participants began by writing a short essay describing what they want to be remembered for by future generations...The essay-writing task was omitted in the control condition, which otherwise followed the same procedure as the legacy condition." The writing task will be copied verbatim from the project's supplemental materials online.

**Environmental Behaviors**
As per the original experiment, "Participants next answered two sets of questions, one assessing their beliefs about climate change and the other their willingness to take proenvironmental action. Climate-change beliefs were measured using the average score of four randomly ordered items (α = .88; e.g., “I feel a responsibility to reduce my personal contribution to climate change”). Participants responded to each statement on a 7-point scale ranging from 1 (strongly disagree) to 7 (strongly agree). Similarly, proenvironmental behavioral intentions were measured using the average score of six items that asked participants how often they intend to perform actions to help mitigate climate change over the next month (α = .76; e.g., “Buy green products instead of regular products”); responses were made on a scale from 1 (never) to 6 (all the time). Following the belief and intention questions, participants were given the opportunity to donate part of their experimental bonus to an environmental organization..."

**Manipulation Check - Legacy Motives**
Following the original experiment, "This measure consisted of the average score of three items relating to legacy motives (α = .82): (a) “It is important to me to leave a positive legacy,” (b) “It is important for me to leave a positive mark on society,” and (c) “I care about what future generations think of me.” Participants indicated the extent to which each statement described them on a scale from 1 (not at all) to 6 (a great amount). This legacy-motives scale was placed at the end of the survey..."


###Analysis Plan
As per the original paper, no participants will be excluded from analysis. In addition, although additional analysis was performed controlling for a range of demographic variables (to show the robustness of the finding), the original analysis examines the effect of condition on the various DV's, without controlling for demographic variables. 

Linear regressions will be performed to examine the effect of the legacy prime on legacy motives, climate change beliefs, and behavioral intentions. 

In addition, mediation analysis will be conducted using both a sobel's z test, and using bootstrapping as suggested by Preacher & Hayes, 2008, with 5,000 samples. Specifically, it is predicted that legacy motives mediates the relationship between condition (legacy prime/no legacy prime) and both climate change attitudes and intentions.

Finally, analysis will be conducted with the donation measure, examining both the effect of condition, and legacy motives as mediator. 

###Differences from Original Study
In the interest of time, we may need to shorten the essay writing task. In the original study, participants spent an average of 6.5 minutes writing their legacy essays. However, this may need to be shortened. If the task still passes the manipulation check, then it is not expected to have any effect on the results. 

##(Post Data Collection) Methods Addendum

###Actual Sample
Sample size, demographics, data exclusions based on rules spelled out in analysis plan

###Differences from pre-data collection methods plan
Any differences from what was described as the original plan, or “none”.


##Results

###Data preparation
Data preparation following the analysis plan.

###Confirmatory analysis
The analyses as specified in the analysis plan

###Exploratory analyses
Any follow-up analyses desired (not required).

##Discussion

###Summary of Replication Attempt
Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

###Commentary
Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.

